---
title: "Exercise 2"
author: "Victor Ying"
date: "10/6/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plotly)
library(tidyverse)
```

##Follow these steps to complete the exercise:

* **As in previous exercises, you should fork and clone this repository:**
Done.

* **Create an new R Markdown (.Rmd) file in this project called index.Rmd (so that we can easily create a website):**
Done.

* **Using the available documentation, create a chart of your choice, and add annotations using Plotly (in a code block):**
```
p <- plot_ly(starwars2, y = ~mass, color = I("dodger blue"),
             alpha = 0.5, boxpoints = "outliers")
p1 <- p %>% add_boxplot(x = "Species")
p2 <- p %>% add_boxplot(x = ~species)
subplot(
  p1, p2, shareY = TRUE,
  margin = 1
) %>% hide_legend()
```

* **Write a short paragraph, and then show your plot in your Markdown file **  
Okay, here is my paragraph.  I don't have much to say.  I'm just trying to write four complete sentences.  I hope you like my Starwars plot:
```{r, echo=FALSE}
starwars2 <- filter(starwars, name!="Jabba Desilijic Tiure")
p <- plot_ly(starwars2, y = ~mass, color = I("dodger blue"),
             alpha = 0.5, boxpoints = "outliers")
p1 <- p %>% add_boxplot(x = "Species")
p2 <- p %>% add_boxplot(x = ~species)
subplot(
  p1, p2, shareY = TRUE,
  widths = c(.3, .7), margin = 1
) %>% hide_legend()
```


* **Knit your HTML file **  
Done.

* **Add and commit your changes to Git (on your terminal) and push them to GitHub:**  
Okay.

* **View your new interactive website at [username-placeholder.github.io/m12-plotly/exercise-2](http://username-placeholder.github.io/m12-plotly/exercise-2) (assuming that you have set the  master branch to be hosted, as described in exercise-1)**
